---
output: html_document
---
## Homework 3

<!--
You can use the example3.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework3.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->

```{r}
dat<-read.csv("example3.csv")
```
"major", "year", "conservativism"


## Students varied grade level and Conservativism

Check the structure of the data.
-->
## Next we check out the structure of the data

```{r}
str(dat)
```

Find the mean, median, and standard deviation using the sd() function
for the overall level of conservatism.
-->
## mean, median and standard deviation for the overall level of conservatism
```{r}
mean(dat$support)

median(dat$support)

var(dat$support)
```
## From the previous analysis we can see that the mean was 63.4 the median was 67.0 and the standard deviation listed as a variance was 171.6

<!--
Find the mean level of support for freshmen only.
-->

## Mean level of support for freshmen only

```{r}
mean(dat$support[dat$year=="freshmen"])
```
## The mean level of support for freshmen is NaN```
<!--
Find the mean level of support for male business students only.
-->
## Mean level of support for male business students only
```{r}
mean(dat$support[dat$gender=="male business students" & dat$party=="democrat"])
```
