## Example 6

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
--



```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```


<!--
Read in the homework6.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
The fabricated data are supposed to approximate how people perform
in different types of visual searches. Specifically, we're 
comparing performance in feature searches (e.g. looking for a red
X among green Xs) and conjunction searches (e.g. looking for a red
X among green Xs and red Os). We're also looking at how the number
of distractors within the search display effect our data.
-->

```{r}
dat<-read.csv("homework6.csv")
```


<!--
Check the structure of the data and change any variables that should
be factor variables into factor variables
-->

```{r}
str(dat)
```


<!--
Perform a one-way between-subjects ANOVA examining for effects of 
the the number of distractors for the conjunction searches only.
Also create a line graph to help you interpret the results of your
analysis.
-->

From the structure we can see that distractors, subject, and subject2
should all be factor variables. So let's fix that.

```{r}
dat$distractor<-as.factor(dat$distractors)
dat$subject<-as.factor(dat$subject)
dat$subject2<-as.factor(dat$subject2)


temp<-dat[dat$type=="conjunction",]%>%group_by(distractors)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(rt)))

f<-ggplot(temp, aes(x=as.factor(distractors),
                    y=means,
                    group=1))+
  geom_line(size=1)+
  geom_point(size=2)+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("rt for searches as a function of distractors")+
  labs(x="Distractors",y="RT")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```

```{r}
summary(aov(rt~distractors, data=dat[dat$type=="conjunction",]))
```


<!--
Perform a one-way within subjects ANOVA on the same data you analyzed
earlier. Tip: use subject as the subjects variable for this analysis.
-->


```{r}
summary(aov(rt~distractors+Error(subject/distractors), data=dat[dat$type=="conjunction",]))
```


<!--
Perform a between-subjects ANOVA examining for the effects of and
interactions between the number of distractors and the search type.
Make sure to interpret your results.
-->

Now, I'll perform a between-subjects 2-way ANOVA looking for effects
of and interactions between distractors and type.

```{r}
 summary(aov(rt~distractors*type, data=dat))
```


<!--
Create a line graph and a grouped bar graph to help us interpret
the results of the previous analyses. Include error bars in your
figures.
-->

To help me interpret the earlier analyses, I'll create line and
grouped bar graphs for the data I analyzed. But first I need to
summarize the data.

```{r}
temp<-dat%>%group_by(distractors,type)%>% 
  summarize(means=mean(rt), 
              sems=sd(rt)/sqrt(length(rt)))

f<-ggplot(temp, aes(x=distractors,
                    y=means,
                    group=type,
                    color=type))+
  geom_line(size=1)+
  geom_point(size=2)+
  scale_color_manual(values=c("darkgreen","red"),
                     name="type",
                     breaks=c("feature","conjunction"),
                     labels=c("feature", "conjunction"))+
  geom_errorbar(aes(ymax=means+sems, ymin=means-sems),width=.2)+
  ggtitle("Rt for searches as a function of distractors and type")+
  labs(x="List Position",y="Rt")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f

f<-ggplot(temp, aes(x=factor(distractors),
                    y=means,
                    fill=type))+
  geom_bar(stat="identity",position=position_dodge())+
  scale_fill_manual(values=c("darkgreen","red"),
                     name="type of search",
                     breaks=c("feature","conjunction"),
                     labels=c("feature ", "conjunction"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2,
                position=position_dodge(.9))+
  ggtitle("Rt for searches as a function of distractors and types")+
  labs(x="Distractors",y="Rt")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f
```



<!--
Interpret the statistical results in light of the figures.
-->

From the figures and earlier analyses we can see that people
generally recognize the object they are looking for, for example a red"O" in a group of green "O"'s or red "X's" better when the distractor is just a conjunction instead of a feature. We can also see that in general participants performed
worse when they had the feature distractor. Most
importantly, the interaction reveals that individuals have a quicker response time when exposed to the conjunction.The response times for conjunctions are quite a bit more (faster Rt) than with the feature.


<!--
Perform a within-subjects two-way ANOVA examining for the effects
of and interactions between number of distractors and search type.
Tip: use subject as the subject's variable for this analysis.
Interpret the results of the analysis based on the statistical
results and your earlier figures.
-->

Here I'm performing a within-subjects two-way ANOVA to examine for
the effects of and interactions between distractorsand
type.

```{r}
 summary(aov(rt~distractors*type+ 
               Error(subject/(distractors*type)),data=dat))
```


From the analyses and the figures we can see that generally people have a shorter response time when the variable is conjunction versus feature, F(1,7) =
1626, p < .05. We can also see that people are generally more
able to have a quicker response time with the conjunction rather than the feature F(1626,57.27) = 57.3, p < .05. Finally,
we can see that those without a feature perform best for the
words at the beginning and end of the lists while, those with a
conjucntion perform best for the response time F(1,7) = 1626, p < .05.

<!--
Finally conduct and interpret the results of a mixed ANOVA in which
number of distractors varies within subjects and the type of search
varies between subjects. Make sure to interpret your results. Tip:
use subject2 as your subject's variable for this analysis.
-->

Finally, I'll conduct a mixed ANOVA. 


```{r}
summary(aov(rt~distractors*type+
              Error(subject2/distractors),
            data=dat))
```

From our anlyses, we can see that individuals without feature performed better than those who had, F(1,22) = 4.6, p < .05, which is a significant result.
Additionally, participants generally performed better with the conjunction variable F (1,22) and = (17.93)= 17.9 than with the feature variable (1,7) F=118 with p < .05
